Bayesian Mixed Effects Models - Training Data

### 2024-03-11 Analysis/brms_learning.qmd
brms learning model fitting script

>>>>

prior <- c(
  prior(normal(200, 200), lb=0, nlpar = "a"),
  prior(normal(800, 300), lb=0,  nlpar = "b"),
  prior(normal(.3, .2), lb=0,  nlpar = "c")
)

prior <- c(
  prior(normal(200, 200), lb=0, nlpar = "a"),
  prior(normal(800, 300), lb=0,  nlpar = "b"),
  prior(lognormal(.3, .2), lb=0,  nlpar = "c")
)

nlform <- bf(
  dist ~ a + (b - a) * exp(-c * gt.train),
  a ~ 0 + condit + (1|bandInt) + (1|id), 
  b ~ 0 + condit + (1|bandInt)  + (1|id), 
  c ~ 0 + condit + (1|id), 
  nl = TRUE 
)

fit <- brm(
  formula = nlform,
  data = e1 |> filter(expMode2=="Train"),
  family = gaussian(), # Assuming 'dist' is continuous; adjust as needed
  prior = prior,
  silent=0,
  control = list(adapt_delta = 0.90), # Adjust for convergence issues if necessary
  chains = 2, iter = 600 # Adjust these values based on your needs
)

summary(fit)
bayestestR::describe_posterior(fit)
coef(fit)$id |> as_tibble(rownames="id") |> select(id,starts_with("Esti")) |> print(n=15)

```{r}
walk(c("brms","dplyr"), conflict_prefer_all, quiet = TRUE)
options(brms.backend="cmdstanr",mc.cores=2)

nlform <- bf(
  dist ~ a + (b - a) * exp(-c * gt.train),
  a ~ 1 + condit + vb, # a as a function of condit and vb
  b ~ 1 + condit + vb, # b as a function of condit and vb
  c ~ 1 + condit + vb, # c as a function of condit and vb
  nl = TRUE # Indicates this is a non-linear model
)

# Define the prior (adjust according to your domain knowledge)
prior <- c(
  prior(normal(150, 50), nlpar = "a"),
  prior(normal(800, 200), nlpar = "b"),
  prior(normal(.3, .1), nlpar = "c")
)

fit <- brm(
  formula = nlform,
  data = e1 |> filter(expMode2=="Train"),
  family = gaussian(), # Assuming 'dist' is continuous; adjust as needed
  prior = prior,
  control = list(adapt_delta = 0.95), # Adjust for convergence issues if necessary
  chains = 2, iter = 1000 # Adjust these values based on your needs
)

# Display the summary of the model
summary(fit)

# To check diagnostics
plot(fit)

formula <- bf(dist ~ a + (b - a) * exp(-c * gt.train),
              a + b + c ~ 1 + condit*vb,
              nl = TRUE)

# Fit the model with brms
fit <- brm(formula,
           data = filtered_data,
           family = gaussian,
           chains = 4, cores = 4,
           control = list(adapt_delta = 0.99, max_treedepth = 15),
           iter = 4000, warmup = 1000)
```

### OLD
